Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-24 2019/NUMTA_Barkalov/Special Issure/article.tex
Added Conclusion

>>>>

\section{Conclusion}
	In this paper, a method for solving the Lipschitz optimization problems, which constitute an important class of the global optimization problems, was considered. In applied global optimization problems, the functions are usually defined as the “black boxes”. Consequently, the values of the Lipschitz constant for them are unknown \textit{a priori}, which makes their estimation one of the key problems when constructing the Lipschitz optimization methods.

	A correct estimate of the Lipschitz constant is especially important in solving constrained problems since the feasible domain in these problems has a complex structure, which is largely determined by the values of the constants for the constraints of the problem. An underestimate of the true value of the constant may lead to the loss of convergence of the method to the global optimizer whereas an overestimated value results in a slow convergence to the solution of the problem.

	This paper proposes an algorithm for solving global optimization problems with non-convex constraints, which uses two Lipschitz constant estimates, one of which is considerably larger than the other.  The larger estimate ensures global convergence and the smaller one reduces the total number of trials required to find the global optimizer. The choice of the estimate to be used in the rules of the algorithm is performed automatically. The conditions of convergence for the algorithm with dual estimate of the Lipschitz constant were found. The numerical experiments carried out on a series of several hundred constrained global optimization test problems demonstrated the effect of reduction of the number of search trials in the index algorithm with dual estimate of the Lipschitz constant as compared to the original version of the algorithm.

	Further research areas include the use of the dual estimate of the Lipschitz constant in parallel algorithms, which can be constructed with the use of various schemes for  dimensionality reduction and  for parallelization of the computations \cite{Strongin2018}.
